---
title: "Songinfo"
author: "Hovanes Keseyan"
date: "December 13, 2017"
output: word_document
geometry: margin=.75in
---

## Data Preparation

### Load the songs into R

Asks for song locations and loads into R.

```{r songloader, echo=TRUE}
songloader <- function()
{
  n <- readline("How many songs would you like to load? ")
  n <- as.integer(n)
  if(is.na(n)){
    n <- songloader()
  }
  wd <- readline("Working Directory: ")
  #if(is.na(wd)) getwd()
  #else setwd(wd)
  f <- vector(length = n)
  v <- matrix(nrow = n, ncol = 7)
  songs <- list()
  for (i in 1:n) {
    f[i] <- readline("File name: ")
    v[i] <- readline("Set variable name: ")
    songs[[i]] <- read.csv(f[i], header=F, row.names = NULL,
                           col.names = c("track", "time", "type", 4:7), stringsAsFactors=FALSE)
  }

  return(songs)
}
songloader


##ask for directory??
setwd("C:/Users/Hovanes/Desktop/UCR/Project")
##ask for filename??
a = read.csv("createdsong.csv", header=F, row.names = NULL, col.names = c("track", "time", "type", 4:7), stringsAsFactors=FALSE)
```

### Extract data

Start with only the frequency data for now

```{r extract, echo=TRUE}
a_notes = a[a$type==" Note_on_c",]
colnames(a_notes)=c("track", "time", "type", "channel", "note", "velocity")
```

### Convert note on c to note off c

Separate the note on c types that have velocity zero (end note) so it's easier to plot

```{r noteoffc, echo=TRUE}
a_notes_on = a_notes[a_notes$velocity!="0",]
a_notes_off = a_notes[a_notes$velocity=="0",]

a_notes_first6=a_notes_on[a_notes_on$track<=6,]

a_durations <- a_notes_off[a_notes_off$track<=6, "time"] - a_notes_on[a_notes_on$track<=6,"time"]

head(a_notes)
```
---

\pagebreak

---

# Song statistics

### Number of notes: `r nrow(a_notes_first6)`

### Duration (seconds): `r sum(a_durations)/1000`

Number of tracks analyzed: 5

Average number of notes per track: `r nrow(a_notes_first6)/5`

Average seconds per note per track: `r (sum(a_durations)/1000)/(nrow(a_notes_first6)/5)`

Average notes per minute per track: `r (nrow(a_notes_first6)/5)/(sum(a_durations)/1000)*60`

### Derived Tempo: `r (nrow(a_notes_first6)/5)/(sum(a_durations)/1000)*60/4`



---
\pagebreak

# Plots of note frequencies

```{r plotnotes, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
require(ggplot2)
require(methods)

# entire song

a_plot <- ggplot(a_notes_first6, aes(time, note, colour=track, size=abs(a_durations))) + geom_point() + coord_cartesian(xlim = c(0, 2880)) + scale_color_gradient(low="red", high="blue")
a_plot

# 30 second segments

a_plot <- ggplot(a_notes_first6, aes(time, note, colour=track, size=abs(a_durations))) + geom_point() + coord_cartesian(xlim = c(0, 720)) + scale_color_gradient(low="red", high="blue")
a_plot
a_plot <- ggplot(a_notes_first6, aes(time, note, colour=track, size=abs(a_durations))) + geom_point() + coord_cartesian(xlim = c(720, 1440)) + scale_color_gradient(low="red", high="blue")
a_plot
a_plot <- ggplot(a_notes_first6, aes(time, note, colour=track, size=abs(a_durations))) + geom_point() + coord_cartesian(xlim = c(1440, 2160)) + scale_color_gradient(low="red", high="blue")
a_plot
a_plot <- ggplot(a_notes_first6, aes(time, note, colour=track, size=abs(a_durations))) + geom_point() + coord_cartesian(xlim = c(2160, 2880)) + scale_color_gradient(low="red", high="blue")
a_plot
```




